MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38 - Model Selection

### 2020-04-01 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_SALMON_GRCh38.Rmd
remove CQN normalization from salmon model sel

---
title: "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection"
author: "Kelsey Montgomery, Gabriel Hoffman, Thanneer Perumal"
date: "`r date()`"
output: html_document
---

@@

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd",
                                 parentId ="syn21435176",
                                 folderName = "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN")
```

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)
library(R.utils)
library(ggplot2)
library(limma)
library(psych)
library(edgeR)
library(cqn)
library(lme4)
library(biomaRt)
library(variancePartition)
library(synapser)
library(knitr)
library(githubr) # get the package from devtools::install_github('brian-bot/githubr')

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn21435176';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 feature counts with CQN normalisation (ACC and DLPFC)';

thisFileName <- 'MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd'

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='add-dream')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21754352'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL

# Parse gene lengths
gene_lengths = counts[,c("Geneid", "Length")]
counts$Length <- NULL
gene_lengths <- dplyr::rename(gene_lengths, gene_id = Geneid)

@@

#Get Metadata
metadata = 'syn16816488' 
ALL_USED_IDs[length(ALL_USED_IDs)+1] = metadata
metadata = downloadFile_version(metadata, version = 16)  %>% 
  dplyr::select(Individual_ID, Institution, Reported_Gender, Sex, 
                Ethnicity, ageOfDeath, `PMI_(in_hours)`, Dx,
                Sample_RNA_ID, one_of('rnaSeq_isolation:RIN',
                                      'rnaSeq_report:Ribozero_Batch', 'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:Flowcell_Batch','rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned'))

@@

# Gender
# vcd::mosaic(~ Gender + Dx.Tissue, data = COVARIATES)
```
### Filter genes
Remove genes that have less than 1 cpm counts in at least 50% of samples per Dx.Tissue. Also remove genes with missing gene length and percentage GC content
```{r cpmnormalisation}
counts$gene_id = NULL

@@

genesToAnalyze = unlist(genesToAnalyze) %>% 
  unique() %>%
  intersect(GENE.GC.CONT$gene_id[!is.na(GENE.GC.CONT$percentage_gene_gc_content)]) %>%
  intersect(gene_lengths$gene_id[!is.na(gene_lengths$Length)])

@@

### Library Normalisation
Initial library normalisation usign cqn
```{r cqn}
# Compute offset for gene length and gc content
gene_lengths = tibble::column_to_rownames(gene_lengths, var = 'gene_id') %>% as.data.frame()
CQN.GENE_EXPRESSION = cqn(NEW.COUNTS, 
                          x = GENE.GC.CONT[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gene_gc_content'],
                          lengths = gene_lengths[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'Length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
```

### Co-expression distribution
Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(CQN.GENE_EXPRESSION$E))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Sample clustering
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis', cache=FALSE}
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E, scale.=T, center = T)

@@

tree = hclust(as.dist(t(CQN.GENE_EXPRESSION$E)))
cols = WGCNA::labels2colors(COVARIATES.tmp);

@@

### Distribution of samples (log cpm)
```{r lcpm.dist, cache=FALSE}
# Plot abberent distribution of logcpm counts
tmp1 = (CQN.GENE_EXPRESSION$E) %>%
  rownameToFirstColumn('gene_id') %>%
  tidyr::gather(SampleID, logCPM, -gene_id) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID'))

p = ggplot(tmp1, aes(x = logCPM, color = SampleID)) + geom_density() 
p = p + theme_bw() %+replace% theme(legend.position = 'NONE') + facet_grid(.~Dx.Tissue, scale = 'free')
p
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

@@

### Model Identification
```{r fxn}
# Function to fit a mixed effect model and return BIC
fitMixedEffectModel <- function(varsToFit, groupingVar, lcpm, cnt, covars){

  # Get design matrix
  designMat = getDesignMatrix(covars[colnames(lcpm), varsToFit, drop=F], Intercept = F)
  designMat = designMat$design[,linColumnFinder(designMat$design)$indepCols]

@@

  modelBIC = foreach::foreach(i = 1:dim(lcpm)[1],
                              .combine = rbind,
                              .packages = c('lme4', 'dplyr'),
                              .export = c('voomWeights')) %dopar% {

                                # Perform weighted mixed linear models for every gene
                                expr = data.frame(Gx = lcpm[i,])
                                data = cbind(expr,
                                             designMat[rownames(expr),],
                                             Individual_ID = groupingVar)
                                formula = paste(setdiff(colnames(data), c('Gx', 'Individual_ID')), collapse = '+') %>%
                                  paste('Gx ~',.,'+ (1|Individual_ID)', collapse = ' ')

                                weights = voomWeights[i,]
                                BIC = NA
                                tryCatch({
                                  mdl = lmer(formula = formula, 
                                             data = data, 
                                             weights = weights)
                                  BIC = BIC(mdl)
                                }, error = function(e){
                                  BIC = NA
                                })
                              return(data.frame(ensembl_gene_id = rownames(lcpm)[i],
                                                BIC = BIC))
                            }
  return(modelBIC)
  }
# Function to select covariates in a step-wise regression fashion
selectCovarsToAdjust <- function(covarsToSelect, adjustCovars, covars, lcpm, cnt, baseModelBIC){

@@

                            # Fit a mixed effect linear model and get all BIC
                            modelBIC = fitMixedEffectModel(c(adjustCovars, covarsToSelect[i]),
                                                           covars[colnames(cnt),'Individual_ID'], 
                                                           lcpm, 
                                                           cnt, 
                                                           covars) %>%
                            plyr::rename(c('BIC' = covarsToSelect[i]))

@@

  return(varsSelected)
}
```
#### Phase I (clinical, ancestry and sample specific technical variables)
```{r phase1}
# Fit a base model with the following covariates
adjust.covars = c('Dx.Tissue')
baseModelBIC = fitMixedEffectModel(adjust.covars, 
                                   COVARIATES[colnames(NEW.COUNTS),'Individual_ID'], 
                                   CQN.GENE_EXPRESSION$E, 
                                   NEW.COUNTS, 
                                   COVARIATES) %>%
  dplyr::rename(baseModel = BIC)
# Iteratively identify covariates in phase I
phase1.covars = c('Institution', 'Reported_Gender', 'PMI', 'ageOfDeath', 'RIN', 'RIN2', 'EV.1', 'EV.2', 'EV.3', 'EV.4', 'EV.5')
vars.selected = selectCovarsToAdjust(phase1.covars, adjust.covars, 
                                     COVARIATES, CQN.GENE_EXPRESSION$E, 
                                     NEW.COUNTS, baseModelBIC)
adjust.covars = c(adjust.covars, vars.selected)
```
Clinical and technical variables selected in phase I are `r paste(adjust.covars, collapse = ', ')`

#### Phase II (batch effects)
```{r phase2}
# Fit a base model with the following covariates
baseModelBIC = fitMixedEffectModel(adjust.covars, 
                                   COVARIATES[colnames(NEW.COUNTS),'Individual_ID'], 
                                   CQN.GENE_EXPRESSION$E, 
                                   NEW.COUNTS, 
                                   COVARIATES) %>%
  dplyr::rename(baseModel = BIC)
# Iteratively identify covariates in phase I
phase2.covars = c('LibraryBatch', 'FlowcellBatch')
vars.selected = selectCovarsToAdjust(phase2.covars, adjust.covars, 
                                     COVARIATES, CQN.GENE_EXPRESSION$E, 
                                     NEW.COUNTS, baseModelBIC)
adjust.covars = c(adjust.covars, vars.selected)
```
Clinical, technical and batch variables selected after phase I and II of model identification are `r paste(adjust.covars, collapse = ', ')`

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
# Fit a base model with the following covariates
baseModelBIC = fitMixedEffectModel(adjust.covars, 
                                   COVARIATES[colnames(NEW.COUNTS),'Individual_ID'], 
                                   CQN.GENE_EXPRESSION$E, 
                                   NEW.COUNTS, 
                                   COVARIATES) %>%
  dplyr::rename(baseModel = BIC)
# Iteratively identify covariates in phase I
phase3.covars = c("MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "rRNARate", "TotalReads")
vars.selected = selectCovarsToAdjust(phase3.covars, adjust.covars, 
                                     COVARIATES, CQN.GENE_EXPRESSION$E, 
                                     NEW.COUNTS, baseModelBIC)
adjust.covars = c(adjust.covars, vars.selected)
```

@@

  transcriptNormalizationMethod	= 'CQN',
  transcriptQuantificationMethod = 'featureCounts',
  referenceSet = 'GRCh38'
)

# Code
CODE <- Folder(name = "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN", parentId = parentId)
CODE <- synStore(CODE)

@@

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('CMC_ACC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
COUNT_OBJ = synStore(COUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(COUNT_OBJ, annotations = all.annotations)

# Store logCPM
CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('CMC_ACC_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
LCOUNT_OBJ = synStore(LCOUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(LCOUNT_OBJ, annotations = all.annotations)

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_offset.tsv', sep = '\t', row.names=F, quote=F)
OFFSET_OBJ = File('CMC_ACC_DLPFC_offset.tsv', name = 'Gene length and GC content offset', parentId = CODE$properties$id)
OFFSET_OBJ = synStore(OFFSET_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(OFFSET_OBJ, annotations = all.annotations)
```

|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |

>>>>

---
title: "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38 - Model Selection"
author: "Kelsey Montgomery, Gabriel Hoffman, Thanneer Perumal"
date: "`r date()`"
output: html_document
---

@@

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_SALMON_GRCh38.Rmd",
                                 parentId ="syn21435176",
                                 folderName = "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38")
```

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)
library(R.utils)
library(ggplot2)
library(limma)
library(psych)
library(edgeR)
library(lme4)
library(biomaRt)
library(variancePartition)
library(synapser)
library(knitr)
library(githubr) # get the package from devtools::install_github('brian-bot/githubr')

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn21435176';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 salmon counts (ACC and DLPFC)';

thisFileName <- 'MSSM-Penn-Pitt_ACC_DLPFC_SALMON_GRCh38.Rmd'

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='add-dream')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21869686'
ALL_USED_IDs = counts
counts = readRDS(synGet(counts)$path)
counts = counts$counts

@@

#Get Metadata
metadata = 'syn16816488' 
ALL_USED_IDs[length(ALL_USED_IDs)+1] = metadata
metadata = downloadFile_version(metadata, version = 18)  %>% 
  dplyr::select(Individual_ID, Institution, Reported_Gender, Sex, 
                Ethnicity, ageOfDeath, `PMI_(in_hours)`, Dx,
                Sample_RNA_ID, one_of('rnaSeq_isolation:RIN',
                                      'rnaSeq_report:Ribozero_Batch', 'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:Flowcell_Batch','rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned'))

@@

# Gender
# vcd::mosaic(~ Gender + Dx.Tissue, data = COVARIATES)
```
### Filter genes
Remove genes that have less than 1 cpm counts in at least 50% of samples per Dx.Tissue. Remove genes with percentage GC content
```{r cpmnormalisation}
counts$gene_id = NULL

@@

genesToAnalyze = unlist(genesToAnalyze) %>% 
  unique() %>%
  intersect(GENE.GC.CONT$gene_id[!is.na(GENE.GC.CONT$percentage_gene_gc_content)])

@@

### Library Normalisation
Salmon utilizes sample-specific bias models for transcriptome-wide abundance estimation.

### Co-expression distribution
Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(NEW.COUNTS))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Sample clustering
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis', cache=FALSE}
# Find principal components of expression to plot
PC <- prcomp(NEW.COUNTS, scale.=T, center = T)

@@

tree = hclust(as.dist(t(NEW.COUNTS)))
cols = WGCNA::labels2colors(COVARIATES.tmp);

@@

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(NEW.COUNTS, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

@@

### Model Identification
```{r fxn}
# Function to fit a mixed effect model and return BIC
fitMixedEffectModel <- function(varsToFit, groupingVar, cnt, covars){

  # Get design matrix
  designMat = getDesignMatrix(covars[colnames(cnt), varsToFit, drop=F], Intercept = F)
  designMat = designMat$design[,linColumnFinder(designMat$design)$indepCols]

@@

  modelBIC = foreach::foreach(i = 1:dim(cnt)[1],
                              .combine = rbind,
                              .packages = c('lme4', 'dplyr'),
                              .export = c('voomWeights')) %dopar% {

                                # Perform weighted mixed linear models for every gene
                                expr = data.frame(Gx = cnt[i,])
                                data = cbind(expr,
                                             designMat[rownames(expr),],
                                             Individual_ID = groupingVar)
                                formula = paste(setdiff(colnames(data), c('Gx', 'Individual_ID')), collapse = '+') %>%
                                  paste('Gx ~',.,'+ (1|Individual_ID)', collapse = ' ')

                                weights = voomWeights[i,]
                                BIC = NA
                                tryCatch({
                                  mdl = lmer(formula = formula, 
                                             data = data, 
                                             weights = weights)
                                  BIC = BIC(mdl)
                                }, error = function(e){
                                  BIC = NA
                                })
                              return(data.frame(ensembl_gene_id = rownames(cnt)[i],
                                                BIC = BIC))
                            }
  return(modelBIC)
  }
# Function to select covariates in a step-wise regression fashion
selectCovarsToAdjust <- function(covarsToSelect, adjustCovars, covars, cnt, baseModelBIC){

@@

                            # Fit a mixed effect linear model and get all BIC
                            modelBIC = fitMixedEffectModel(c(adjustCovars, covarsToSelect[i]),
                                                           covars[colnames(cnt),'Individual_ID'], 
                                                           cnt, 
                                                           covars) %>%
                            plyr::rename(c('BIC' = covarsToSelect[i]))

@@

  return(varsSelected)
}
```
#### Phase I (clinical, ancestry and sample specific technical variables)
```{r phase1}
# Fit a base model with the following covariates
adjust.covars = c('Dx.Tissue')
baseModelBIC = fitMixedEffectModel(adjust.covars, 
                                   COVARIATES[colnames(NEW.COUNTS),'Individual_ID'], 
                                   NEW.COUNTS, 
                                   COVARIATES) %>%
  dplyr::rename(baseModel = BIC)
# Iteratively identify covariates in phase I
phase1.covars = c('Institution', 'Reported_Gender', 'PMI', 'ageOfDeath', 'RIN', 'RIN2', 'EV.1', 'EV.2', 'EV.3', 'EV.4', 'EV.5')
vars.selected = selectCovarsToAdjust(phase1.covars, adjust.covars, 
                                     COVARIATES,
                                     NEW.COUNTS, baseModelBIC)
adjust.covars = c(adjust.covars, vars.selected)
```
Clinical and technical variables selected in phase I are `r paste(adjust.covars, collapse = ', ')`

#### Phase II (batch effects)
```{r phase2}
# Fit a base model with the following covariates
baseModelBIC = fitMixedEffectModel(adjust.covars, 
                                   COVARIATES[colnames(NEW.COUNTS),'Individual_ID'], 
                                   NEW.COUNTS, 
                                   COVARIATES) %>%
  dplyr::rename(baseModel = BIC)
# Iteratively identify covariates in phase I
phase2.covars = c('LibraryBatch', 'FlowcellBatch')
vars.selected = selectCovarsToAdjust(phase2.covars, adjust.covars, 
                                     COVARIATES,
                                     NEW.COUNTS, baseModelBIC)
adjust.covars = c(adjust.covars, vars.selected)
```
Clinical, technical and batch variables selected after phase I and II of model identification are `r paste(adjust.covars, collapse = ', ')`

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
# Fit a base model with the following covariates
baseModelBIC = fitMixedEffectModel(adjust.covars, 
                                   COVARIATES[colnames(NEW.COUNTS),'Individual_ID'], 
                                   NEW.COUNTS, 
                                   COVARIATES) %>%
  dplyr::rename(baseModel = BIC)
# Iteratively identify covariates in phase I
phase3.covars = c("MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "rRNARate", "TotalReads")
vars.selected = selectCovarsToAdjust(phase3.covars, adjust.covars, 
                                     COVARIATES,
                                     NEW.COUNTS, baseModelBIC)
adjust.covars = c(adjust.covars, vars.selected)
```

@@

  transcriptNormalizationMethod	= 'salmon',
  transcriptQuantificationMethod = 'salmon',
  referenceSet = 'GRCh38'
)

# Code
CODE <- Folder(name = "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38", parentId = parentId)
CODE <- synStore(CODE)

@@

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('CMC_ACC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
COUNT_OBJ = synStore(COUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(COUNT_OBJ, annotations = all.annotations)
```

|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
